---
output:
  pdf_document: default
  html_document: default
---
# Reading Data

* `read.table`, `read.csv`, for reading tabular data
  + `file`, the name of the file, or a connection
  + `header`, logical indicating if the file ha a header
  + `sep`, a string indicating how the columns are separated.
  + `colClasses`, a character vector indicating the class of each column in the dataset
  + `nrows`, the number of rows in the dataset
  + `comment.char`, a character string indicating the comment character
  + `skip`, the number of lines to skip from the beginning
  + `stringsAsFactors`, should character variables be coded as factors?
  
* `readLines`, for reading lines of a text file
* `source`, for reading in R code files
* `dget`, for reading in R code files
* `load`, for reading in saved workspaces
* `unserialize`, for reading binary objects in R.

# Writing Data

* `write.table`
* `writeLines`
* `dump`
* `dput`
* `save`
* `serialize`

# Handling large datasets

Taking first 100 rows for better memory usage
```{r eval=FALSE}
initial<-read.table("datatable.txt", nrows=100)
classes<-sapply(initial,class)
tabAll<-read.table("datatable.txt",
                   `colClasses=classes)
```
# dput-ing R Objects
```{r}
y<- data.frame(a=1,b="a")
dput(y)
dput(y, file="y.R")
new.y<-dget("y.R")
new.y
```
# Dumping R Objects

```{r}
x<-"foo"
y<-data.frame(a=1,b="a")
dump(c("x","y"), file="data.R")
rm(x,y)     #this will remove x
source("data.R")  #this will again load x from source
x
```






