---
output:
  pdf_document: default
  html_document: default
---
# Subsetting

* [ always returns object of the same class
* [[ is used to extract elements of a list or a data frame; it can only be used to extract a single element and the class of the returned object will not necessarily be alist or data frame
* $ is used to extract elements of a list or data frame by name; semantics are similar to that of [[.

```{r}
x<-c("a","b","c","d","a")
x[1]
x[2]
x[1:4]
x[x>"a"]     #elements in x > "a"
u <- x>"a"   #logical operation showing elements > "a"
u
x[u]         #logical index 
```

# Subsetting Lists

```{r}
x <- list(foo = 1:4, bar = 0.6)
x[1]
x[[1]]
x$bar
x[["bar"]]
x["bar"]
```

```{r}
x <- list(foo = 1:4, bar = 0.6, baz = "hello")
x[c(1,2)]

name <- "foo"
x[[name]]
x$name
x$foo
```
```{r}
x<-list(a=list(10,12,14),b=c(3.14, 2.81))
x[[c(1,3)]]
x[[1]][[3]]
x[[c(2,1)]]
```

# Subsetting a Matrix

```{r}
x<-matrix(1:6,2,3)
x
x[1,2]
x[2,1]
x[1,]
x[,2]
```

## `x[1,2]` gives element rather than a matrix. So, to preserve the matrix we use `drop = FALSE`
```{r}
x<-matrix(1:6,2,3)
x
x[1,2, drop = FALSE] 

```


```{r}
x<-matrix(1:6,2,3)
x
x[1, , drop = FALSE]
```

# Partial Matching

We can use `x$a` instead of `x$aardvark` again and again `x[[a]]` as it will search for `a` in the list which is not present but we can pass the argument `exact=FALSE` to use it similar to the `$` operator
```{r}
x<-list(aardvark=1:5)
x$a
x[["a"]]
x[["a", exact=FALSE]]
```

# Removing NA Values
Create a logical vector which tells you where the NAs
are

```{r}
x<-c(1,2,NA,4,NA,5)
bad<-is.na(x)
x[!bad]
```

```{r}
x<-c(1,2,NA,4,NA,5)
y<-c("a","b",NA,"d",NA,"f")
good<-complete.cases(x,y)
good
x[good]
y[good]
```

```{r}
airquality[1:6,]
good<-complete.cases(airquality)
airquality[good,][1:6,]
```

